Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
more text

When mapping back to the notation used for describing the general architecture of the program synthesizer, 
the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$. 
While the controller precision \todo{update notations} $\langle I_c,F_c\rangle$ is given and fixed, 
we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.

@@

Regarding the latter, we synthesize a safe controller by unwinding the transition system
$k$ steps and picking a controller $K$ and an initial state such that the states at each step do
not violate the safety criteria. This is sound if the current $k$ is below the
completeness threshold, which we assume to be true in the {\sc synthesize} phase.
We also assume some
precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
checks that all these assumptions are sound are performed by subsequent
{\sc verify} stages.

>>>>

When mapping back to the notation used for describing the general architecture of the program synthesizer, 
the controller $K$ denotes $P$ and $(x_0, u_k)$ represents $x$. 
While the controller precision \todo{are these notations updated?} $\langle I_c,F_c\rangle$ is given and fixed, 
we can vary the plant precision $\langle I_p,F_p\rangle$ such that $I_p \geq I_c \wedge F_p \geq F_c$.

@@

 \todo{unclear next: it seems like to select a single initial state here, rather than considering the set thereof - clarify. also, clarify relationship btw k and soundness. }
Regarding the second requirement, we synthesize a safe controller by unwinding the transition system
$k$ steps and by picking a controller $K$ and an initial state, such that the states at each step do
not violate the safety criteria. This is sound if the current $k$ is below the
completeness threshold, which we assume to be true in the {\sc synthesize} phase.
We also assume some
precision $\langle I_p,F_p\rangle$ for the plant and a sampling rate.  The
checks that all these assumptions are sound are performed by subsequent
{\sc verify} stages.
